Automated Formal Synthesis of Provably Safe Digital Controllers for Continuous Plants

### 2019-07-23 automatica/response.tex

\vspace{1em}
{\bf Response: }
We have moved these figures to Section 1 and incorporated them into the Introduction. We are still referring back to these figures from Section 5.

\vspace{2em}

{\bf Comment: } {\itshape
Some other relevant applications of CEGIS to CPS/dynamical systems include: Synthesizing switching logic for
safety and dwell-time requirements in ICCPS, 2010; Synthesis of optimal switching logic for hybrid systems in EMSOFT, 2011, Synthesis of Optimal
Fixed-Point Implementation of Numerical Software Routines in NSV'13, Bridging boolean and quantitative synthesis using smoothed proof search,
POPL'14, Synthesis of fixed-point programs in EMSOFT'13}

\vspace{1em}
{\bf Response: }
We have added a discussion about these applications and results to the related work as follows:

\vskip{2em}
Similarly, 
\cite{liberzon2003hybrid} evaluates the quantization error dynamics and calculates upper and lower
bounds for the possible trajectory of the system, up to a finite time. \rev{Considering the problem of multi-modal
dynamics,~\cite{DBLP:conf/emsoft/JhaST11} uses numerical optimization techniques to learn optimal switching logic for hybrid systems.
The last three} approaches can be placed within the research area known as ``hybrid systems theory.''  
%This technique works for both linear and non-linear systems.
The present contribution distances itself from all these cognate results.

\rev{A large body of work exists on evaluating fixed-point errors and bridging the gap between real value
and fixed-point values in synthesis in other application areas and using other
algorithmic techniques:
Genetic programming has been used to minimise the error in synthesised fixed-point programs~\cite{DBLP:conf/emsoft/DarulovaKMS13};
Smoothed proof search reduces the problem of parameter synthesis under boolean and quantitative 
objectives to a sequence of optimisation problems~\cite{DBLP:conf/popl/ChaudhuriCS14}; Synthesis of 
optimal fixed-point implementations of floating-point numerical software can be done using testing and induction~\cite{DBLP:journals/corr/abs-1302-1920}.
All of these works present potential future applications for CEGIS in synthesising implementations in fixed-point arithmetic.}

@@

\vspace{2em}
{\bf Comment: } {\itshape 
Could you add one example to the end of Section 4 to show $R_1$, $R_2$, $R_3$, $R_4$ for a simple LTI system?

\vspace{2em}
{\bf Comment: } {\itshape 
Section 4 is one the most interesting parts
of the paper and its current presentation is a bit sketchy. What are $m_{ij}$?} }

\vspace{1em}
{\bf Response: }
We apologise for leaving the relatively brief presentation of Jury's criteria in section 4. This is standard
work in the control literature, and so, given the space restrictions, we prioritised our contributions in the write up. 
The values for $R_1$, $R_2$, $R_3$, $R_4$, and the corresponding values in the matrix $M$ are outputted in the counterexample
trace obtained from the synthesis phase in the software tool 
if it is run with full verbosity.

We have added a brief clarification of the notation $m_{ij}$ as follows:

### 2019-07-23 automatica/paper.tex
more response

There are two different problems that arise from finite-precision arithmetic in digital controllers.  
The first is the error caused by the inability to represent the exact state of the physical system, 
while the second relates to rounding and saturation errors during mathematical operations.  
In~\cite{fialho1994stability}, a stability measure based on the error of the digital dynamics ensures that
the deviation introduced by finite-precision arithmetic does not lead to instability.  
\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$-calculus to synthesise directly a digital controller, 
so that selected parameters result in stable model dynamics.  
The analyses in~\cite{DBLP:conf/hybrid/RouxJG15, DBLP:conf/hybrid/WangGRJF16} rely on an
invariant computation on the discrete dynamics using Semi-Definite
Programming (SDP):  while the former contribution uses a bounded-input and bounded-output
(BIBO) notion of stability, the latter employs Lyapunov-based
quadratic invariants.  In both cases, the SDP solver uses floating-point
arithmetic and soundness is checked by bounding the obtained error.  
An alternative is~\cite{park2016scalable}, where the verification of given control code is
performed against a known model by extracting an LTI model of the code via 
symbolic execution: to account for rounding errors, upper bounds of their values are 
introduced in the verification phase.  
The work in~\cite{picasso2003stabilization} introduces invariant sets as a mechanism to
bound the effect of quantization error on stabilization.  
% as an invariant set that always converges toward the controllable set.  
Similarly, 
\cite{liberzon2003hybrid} evaluates the quantization error dynamics and calculates upper and lower
bounds for the possible trajectory of the system, up to a finite time. 
The last two approaches can be placed within the research area known as ``hybrid systems theory.''  
%This technique works for both linear and non-linear systems.
The present contribution distances itself from all these cognate results.

A large body of work exists on evaluating fixed-point errors and bridging the gap between real value
and fixed-point values in synthesis in other application areas and using other
algorithmic techniques; 
Genetic programming has been used to minimise the error in synthesised fixed-point programs~\cite{Darulova};
Smoothed proof search reduces the problem of boolean  a sequence of optimization problems

>>>>

There are two different problems that arise from finite-precision arithmetic in digital controllers.  
The first is the error caused by the inability to represent the exact state of the physical system, 
while the second relates to rounding and saturation errors during mathematical operations.  
In~\cite{fialho1994stability}, a stability measure based on the error of the digital dynamics ensures that
the deviation introduced by finite-precision arithmetic does not lead to instability.  
\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$-calculus to synthesise directly a digital controller, 
so that selected parameters result in stable model dynamics.  
The analyses in~\cite{DBLP:conf/hybrid/RouxJG15, DBLP:conf/hybrid/WangGRJF16} rely on an
invariant computation on the discrete dynamics using Semi-Definite
Programming (SDP):  while the former contribution uses a bounded-input and bounded-output
(BIBO) notion of stability, the latter employs Lyapunov-based
quadratic invariants.  In both cases, the SDP solver uses floating-point
arithmetic and soundness is checked by bounding the obtained error.  
An alternative is~\cite{park2016scalable}, where the verification of given control code is
performed against a known model by extracting an LTI model of the code via 
symbolic execution: to account for rounding errors, upper bounds of their values are 
introduced in the verification phase.  
The work in~\cite{picasso2003stabilization} introduces invariant sets as a mechanism to
bound the effect of quantization error on stabilization.  
% as an invariant set that always converges toward the controllable set.  
Similarly, 
\cite{liberzon2003hybrid} evaluates the quantization error dynamics and calculates upper and lower
bounds for the possible trajectory of the system, up to a finite time. \rev{Considering the problem of multi-modal
dynamics,~\cite{DBLP:conf/emsoft/JhaST11} uses numerical optimization techniques to learn optimal switching logic for hybrid systems.
The last three} approaches can be placed within the research area known as ``hybrid systems theory.''  
%This technique works for both linear and non-linear systems.
The present contribution distances itself from all these cognate results.

\rev{A large body of work exists on evaluating fixed-point errors and bridging the gap between real value
and fixed-point values in synthesis in other application areas and using other
algorithmic techniques:
Genetic programming has been used to minimise the error in synthesised fixed-point programs~\cite{DBLP:conf/emsoft/DarulovaKMS13};
Smoothed proof search reduces the problem of parameter synthesis under boolean and quantitative 
objectives to a sequence of optimisation problems~\cite{DBLP:conf/popl/ChaudhuriCS14}; Synthesis of 
optimal fixed-point implementations of floating-point numerical software can be done using testing and induction~\cite{DBLP:journals/corr/abs-1302-1920}.
All of these works present potential future applications for CEGIS in synthesising implementations in fixed-point arithmetic.}
